---
title: "Homework 5"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 2

### Clean the data

```{r}
tidy_df = 
  tibble(
    files = list.files(path = "data/", full.names = TRUE) 
         ) %>% 
  mutate(data = purrr::map(.x = files, read_csv)) %>% 
  unnest(data) %>% 
  mutate(arm_id = str_extract_all(files, "(exp_\\d+|con_\\d+)")) %>% 
  select(-files) %>% 
  relocate(arm_id) %>% 
  pivot_longer(
             week_1:week_8,
             names_to = "week",
             names_prefix = "week_",
             values_to = "measurement"
             ) %>% 
  mutate_at(vars(week), as.numeric) %>% 
  unnest(arm_id) %>% 
  separate(arm_id, into = c("arm", "subject_id")) 
tidy_df %>% knitr::kable()
```

### Make a spaghetti plot

We can see that for the experiment group, the trend is increasing. For the control group, measurement basically stays the same over weeks.

```{r}
tidy_df %>%
  unite("arm_id", c(arm, subject_id), sep = "_", remove = F) %>%
  ggplot(aes(x = week, y = measurement)) +
  geom_path(aes(color = arm, group = as.factor(arm_id)),alpha = 0.5) +
  labs(
    x = "Week",
    y = "Measurement",
    title = "Measurement over Weeks"
    )
```


## Problem 3

## Generate the simulation 


```{r}
sim_t = function(n = 30, mu = 0, sigma = 5) {
     x = rnorm(n, mean = mu, sd = sigma)
     t_test = t.test(x, conf.int = 0.95) %>% broom::tidy()
     
     t_test
  }
output = vector("list", 5000)
for (i in 1:5000) {
  output[[i]] = sim_t()
}
output %>% bind_rows() %>% head()
```



### A plot showing the power of the test for different true mu


```{r}
sim_mu = function(set){
  output = vector("list", 5000)
  for (i in 1:5000) {
     output[[i]] = sim_t(mu = set)
     }
  power = 
    output %>% 
    bind_rows() %>% 
    janitor::clean_names() %>% 
    select(estimate, p_value) %>% 
    filter(p_value < 0.05) %>% 
    count()
  
  power
}

power_of_test =
  tibble(
    sample_mu = c(0, 1, 2, 3, 4, 5, 6),
    reject_time = map(sample_mu, sim_mu)
  ) %>%  
  unnest(reject_time) %>% 
  mutate(t_power = n/5000)

power_of_test %>% 
ggplot(aes(x = sample_mu, y = t_power)) +
  geom_point(aes(color = sample_mu), alpha = .5, size = 3) +
  geom_smooth(alpha = .5, size = 0.5) +
  labs(
    x = "The true value of mu",
    y = "Proportion of times the null was rejected (the power of the test)",
    title = "The power of the test for different true mu"
    )
```


As the true value of mu (effect size) increases, the power increases. 


### Compare the average estimate of μ^ of all sample and reject-null-sample

```{r}
sim_mu_hat = function(n = 30, mu = 0, sigma = 5) {
     sim_data = tibble(
                           x = rnorm(n, mean = mu, sd = sigma),
                    )
     
     sim_t_test = t.test(pull(sim_data,x), conf.int = 0.95) %>% 
              broom::tidy() %>% 
              janitor::clean_names() %>% 
              select( p_value)
     
     
     sim_data %>% 
     summarize(
      mu_hat_all = mean(x),
      mu_hat_rej = case_when(
        pull(sim_t_test, p_value) < 0.05 ~ mean(x),
        pull(sim_t_test, p_value) >= 0.05 ~ as.numeric("")
      )
    )
}

compare_all_reject = function(set){
  output_mu_hat = vector("list", 5000)
  for (i in 1:5000) {
     output_mu_hat[[i]] = sim_mu_hat(mu = set)
     }
  
  output_mu_hat %>% 
    bind_rows() %>% 
    summarize(
      all_sample = mean(mu_hat_all, na.rm = T),
      reject_sample = mean(mu_hat_rej, na.rm = T)
    )
}

mean_muhat =
  tibble(
    true_mu = c(0, 1, 2, 3, 4, 5, 6),
    hat = map(true_mu, compare_all_reject)
  ) %>%  
  unnest(hat) %>% 
  pivot_longer(
    all_sample:reject_sample,
    names_to = "samples",
    values_to = "average_estimate"
  )

mean_muhat %>% 
 ggplot(aes(x = true_mu, y = average_estimate, group = samples)) +
  geom_point(aes(color = samples), alpha = .5, size = 2) +
  geom_smooth(aes(color = samples), alpha = .5, size = 0.5) +
  labs(
    x = "The true value of μ",
    y = "The average estimate of μ^",
    title = "Compare the average estimate of μ^ of all sample and reject-null-sample"
    )
```
From the plot above we can see that, when true mu equals to 0, the estimate mus of rejecting H0 are spreading on upper side of the true mu 0 until true value of u reaches 4. Thus, the average mu of rejecting H0 closes to true mean as true mean surpasses 4.


 
